High-Throughput Computing on \\ High-Performance Platforms: A Case Study

### 2017-09-10 introduction.tex
pending.

\ifreview
Comments to address in this section:
\begin{enumerate}
	\color{red} 
	\item REVIEWER 1: The introduction is overly verbose and prosaic. The
	praise for LHC collaborations is off-putting, especially as it ignores
	other work. For example, claiming "CMS and ATLAS experiments utilize
	arguably the largest production grade distributed computing solutions"
	disregards the obvious commercial contenders. By blatantly excluding
	obvious comparisons, it raises the question how much other work is
	ignored. \jhanote{Added "academic" after arguably. Any more?}
\end{enumerate}
\fi

>>>>

% \ifreview
% Comments to address in this section:
% \begin{enumerate}
% 	\color{red} 
% 	\item REVIEWER 1: The introduction is overly verbose and prosaic. The
% 	praise for LHC collaborations is off-putting, especially as it ignores
% 	other work. For example, claiming "CMS and ATLAS experiments utilize
% 	arguably the largest production grade distributed computing solutions"
% 	disregards the obvious commercial contenders. By blatantly excluding
% 	obvious comparisons, it raises the question how much other work is
% 	ignored. \jhanote{Added "academic" after arguably. Any more?}
% \end{enumerate}
% \fi
